\documentclass[12pt,letterpaper]{article}
\usepackage{tabularx}
\usepackage{tabulary}
\usepackage{enumitem}
\usepackage{url}
%\usepackage{fullpage}
\usepackage[top = 1in, bottom = 1in, right = 1.15in, left = 1.15in]{geometry}

\renewcommand{\labelitemi}{$$}
\newcommand{\sectionhead}[1]{\begin{flushleft}\large\bf{#1}\vspace{.1cm}\hrule\end{flushleft}}

\begin{document}
\begin{center}
\textbf{Tod Stewart Van Gunten}\vspace{0.3cm}
\end{center}

\noindent
\begin{tabularx}{\textwidth}{@{}Xr@{}}
	University of Edinburgh & \url{todvangunten.com}\\
	Department of Sociology & \texttt{tvangun@ed.ac.uk} \\
	15a George Square & +44 (0) 131 650 4637 (office)  \\
	Edinburgh EH8 9LD, United Kingdom&\\
\end{tabularx}


\sectionhead{Employment}
\begin{tabulary}{.96\textwidth}{@{}p{2.5cm} L}
	
2024--present & Senior Lecturer in Sociology, University of Edinburgh \vspace{0.2cm}\\

2017--2024	& Lecturer in Economic Sociology, University of Edinburgh \vspace{0.2cm}\\

2015--2017 & Research Fellow, Max Planck Institute for the Study of Societies, Cologne, Germany\vspace{0.2cm}\\

2012--2015 & Junior Research Fellow, Carlos III-Juan March Institute for the Social Sciences, and Visiting Professor, Carlos III University, Madrid, Spain\vspace{0.2cm}\\

%& \footnotesize \textit{*UK equivalent to US assistant professor}\vspace{0.2cm}\\

%& \footnotesize \textit{*Formerly the Center for Advanced Studies in the Social Sciences (CEACS) of the Juan March Institute}\\
\end{tabulary}

\sectionhead{Education} 
\begin{tabulary}{.97\textwidth}{@{}p{2.5cm}  L}

2012 & Ph.D. Sociology, University of Wisconsin-Madison\vspace{0.2cm} \\

%& \hangindent=2.9cm \emph{Dissertation:} \hspace{2pt} ``Power and Pesos: Bureaucracy, Expertise and the Politics of Money in Mexico and Argentina'' \\
%& \hangindent=2.9cm \emph{Committee:} \hspace{12pt}
%Erik Olin Wright (chair), John Levi Martin, Gay Seidman, Joan Fujimura, Menzie Chinn (economics)\vspace{0.2cm}\\

2005 & M.A. Humanities and Social Thought, New York University\vspace{0.2cm}\\

%& \hangindent=2.9cm \emph{Thesis:} \hspace{29pt}
%``Money and Morality in Early Capitalism: The School of Salamanca's Analysis of Exchange'' (Advisor: Craig Calhoun)\vspace{0.2cm}\\

2000 & B.A. Sociology (with honors), Whitman College \\
\end{tabulary}

\sectionhead{Research Interests}
\begin{list}{\labelitemi}{\leftmargin = 5px}
	\item Comparative economic and political sociology; social networks; organizations; globalization; sociological theory; sociology of knowledge; Latin America and Southern Europe
\end{list}

%\newpage

\sectionhead{Peer-reviewed publications}
\begin{tabulary}{.97\textwidth}{@{}p{2.5cm}  L}
2024 & ``Elite Politics and Economic Crisis: Hyperinflation in Argentina, 1989-1990.'' Political Power and Social Theory 41 (Elites, Nonelites and Power: The Critical Legacy of Elite Theory from Marx to Lachmann, and then Beyond, edited by Rebecca Jean Emigh and Dylan Riley).	\\
2023 & ``Mapping Economists' Belief Spaces Using Survey Data.''  \OE conomia -- History / Methodology / Philosophy 13 (2), Special Issue on Quantitative and Computational Approaches in the Social Study of Economics.	\\
2023 & ``Are Economists Overconfident? Ideology and Uncertainty in the Economics Profession'' (with Austin Kozlowski).  \textit{British Journal of Sociology}.  \url{https://doi.org/10.1111/1468-4446.13001}\\
\end{tabulary}
\begin{tabulary}{.97\textwidth}{@{}p{2.5cm}  L}
2022 & ``Analysing online social networks.''  \textit{Doing Research Online} (SAGE Research Methods collection, 2022).  \\
2021 & ``Visualizing the network structure of Covid-19 in Singapore. \textit{Socius: Sociological Research for a Dynamic World}. \url{https://journals.sagepub.com/doi/10.1177/23780231211000171}\vspace{0.2cm}\\	
2020 & ``The inversion of the 'really big trade-off': Homeownership and pensions in long run perspective'' (with Sebastian Kohl.) \emph{West European Politics} 43(2).  Published online 2019.  \url{doi.org/10.1080/01402382.2019.1609285}.\vspace{0.2cm}\\  & Re-published as chapter 7 of \textit{Bricks in the wall: The politics of housing in Europe}, edited by Alison Johnston and Paulette Kurzer (Routledge, 2021) \vspace{0.2cm}\\
2018 & ``Varieties of indebtedness: Financialization and mortgage market institutions in Europe'' (with Edo Navot).  \emph{Social Science Research} 70.  \url{doi.org/10.1016/j.ssresearch.2017.11.005}\vspace{0.2cm}\\
2017 &``Washington dissensus: Ambiguity and conflict at the International Monetary Fund.'' \emph{Socio-Economic Review} 15(1).  Published online 2015.  \url{https://doi.org/10.1093/ser/mwv032}\vspace{0.2cm} \\
2016 & ``Consensus, Polarization and Alignment in the Economics Profession'' (first author with John Levi Martin and Misha Teplitsky). \emph{Sociological Science} 3.  \url{doi.org/10.15195/v3.a45}\vspace{0.2cm} \\
%& \emph{General interest summary: ``The IMF and global exchange rates: dissensus in Washington,'' Oxford University Press blog, \url{http://blog.oup.com/2016/03/imf-global-exchange-rates/}}\vspace{0.2cm}\\
2015 & ``Cohesion, Consensus and Conflict: Technocratic elites and financial crisis in Mexico and Argentina.'' \emph{International Journal of Comparative Sociology} 56(5).  \url{doi.org/10.1177/0020715215626238} \vspace{0.2cm}\\
\end{tabulary}
\begin{tabulary}{.97\textwidth}{@{}p{2.5cm}  L}
2015 &``Cycles of polarization and settlement: diffusion and transformation in the macroeconomic policy field.'' \emph{Theory and Society} 44(4).  \url{http://doi.org/10.1007/s11186-015-9253-8}\vspace{0.2cm}\\
2012 &``Charisma, status and gender in groups with and without gurus'' (second author with John Levi Martin and Benjamin Zablocki). \emph{Journal for the Scientific Study of Religion} 51(1). \url{https://doi.org/10.1111/j.1468-5906.2011.01633.x}\vspace{0.2cm}\\
\end{tabulary}

\newpage

\sectionhead{Work in progress}
\begin{list}{\labelitemi}{\leftmargin = 5px}

\item ``Relational herding in financial markets: Mortgage securitization and the Spanish banking crisis'' (under review, with Jacob Habinek)

\item``Brokers, Clients and Elite Political Networks in Mexico.''  Working paper: \url{osf.io/preprints/socarxiv/vb5gx}


%\newpage


\end{list}

\sectionhead{Other publications}
\begin{tabulary}{.97\textwidth}{@{}p{2.5cm}  L}
	
2022 & ``Global Hit-Making on Spotify.''  Creative Informatics Blog. \url{https://creativeinformatics.org/research/global-hit-making-on-spotify/} \\
	
2021 & ``Using network visualization to understand the spread of Covid-19.''  Covid-19 perspectives blog.  \url{https://tinyurl.com/4af5ktzj}\vspace{0.2cm} \\	
	
2020 & ``Review of Gregory Fuller, \emph{The Political Economy of Housing Financialization.}  \emph{Intergenerational Justice Review}	6 (1).  \url{http://www.igjr.org/ojs/index.php/igjr/article/view/797}\vspace{0.2cm}\\

2016 & ``Economists are just like the rest of us.  Their views on controversies line up with their ideologies.''  Monkey Cage blog, Washington Post, Dec. 13. Also published on the ASA Work in Progress blog. \url{http://tinyurl.com/jv2nxq2}\vspace{0.2cm}\\

2016 & ``The IMF and global exchange rates: dissensus in Washington,'' Oxford University Press blog, \url{http://tinyurl.com/jg7sae9}\vspace{0.2cm}\\

2013 & ``Economic expertise in hard times.''  Infolibre (Spain; published in English and Spanish), \url{http://tinyurl.com/hy3378x}\vspace{0.2cm}\\

2010 & ``Review of Martin Wolf, \emph{Fixing Global Finance}.'' \emph{Journal of World Systems Research} 16(2).\vspace{0.2cm}\\
\end{tabulary}


\sectionhead{Invited Presentations}
\begin{list}{\labelitemi}{\leftmargin = 5px}
	
\item ``Consensus and ideology in expert communities: The case of economics'' John F. Kennedy Institute, Free University of Berlin, October 2023 and Centre for Science and Technology Studies (CWTS), Leiden University, November 2023.
	
\item ``Where does power come from?  Elite networks and the presidential succession in Mexico.''  Mannheim University Seminar Series, November 2020 (remote).	

\item ``The economics agora online: Open surveys and the politics of expertise''.  Keynote address at the Digital Day of Ideas, University of Edinburgh, May 2018.

\item ``Over-confident hedgehogs?  Subjective confidence and political ideology in teh economics profession''.  London School of Economics Sociology Seminar Series, March 2018.

\item``Power and pesos: bureaucracy, expertise and the politics of money''.  Cultures of Economic Expertise workshop, London School of Economics, September 2017.

\item``Brokers, Clients and Elite Political Networks in Mexico.''  Centro de Investigaci\'on y Docencia Econ\'omicas (CIDE), Mexico City, October 2015; University of Kiel, October 2016; and Institute for Analytical Sociology, Link{\"o}ping University, Sweden, May 2017.

\item``The Portfolio Society in Europe: Financial Intensification and Household Debt in Six European Countries.'' Babies, Bonds and Buildings workshop, Central European University, Budapest, May 2015.

\item``A Paradox of Bureaucratic Autonomy: Central Bank Legitimacy, Transparency and Commitment.'' Center for Social and Constitutional Studies, Madrid, December 2013. 

\item``Washington Dissensus? Ambiguity and Conflict at the International Monetary Fund.'' University of Edinburgh, February 2013.
\end{list}

%\newpage

\sectionhead{Conference Papers}
\begin{list}{\labelitemi}{\leftmargin = 5px}
	
\item Elite polarization in Argentina: A legislative cosponsorship approach.''  Carlos III-Juan March Conference, Carlos III University (Madrid) and International Network for Social Network Analysis Sunbelt Conference, June 2024	
	
\item ``Where does power come from?  Elite networks and the presidential succession in Mexico.''  American Sociological Association, held online, August 2020.

\item ``Credit and the welfare state: Trade-off and complementarity theories in long-run comparative perspective'' (with Sebastian Kohl).  American Sociological Association, held online, August 2020.

\item ``Relational Herding in Financial Markets: Mortgage Securitization and the Spanish Banking Crisis.''  American Sociological Association, New York, August 2019

\item ``The demise of the `really big trade-off': Homeownership and pensions in long-run perspective.  Presented at the Council for European Studies, Madrid, June 2019 and American Sociological Association, New York, August 2019.

\item``The Diffusion of Financial Exuberance: Securitization in the Spanish Banking Sector.''  Research report presented at the workshop Financial Innovation, Diffusion and Institutionalization: the Case of Securitization, Max Planck Institute for the Study of Societies, Cologne, June 2016.

\item``Do Housing Bubbles Redistribute Wealth? Evidence from Spain.''  Presented at the workshop Inequality: the Wealth-Credit-Housing Nexus and its Political Consequences, Max Planck-Sciences Po Center on Coping with Instability in Market Societies (MaxPo), Paris, April 2016.

\item``The Portfolio Society in Europe: Financial Intensification and Household Debt in Six European Countries.'' Presented at the Annual Meeting of the Society for the Study of Socio-Economics, London, July 2015.

\item``Brokers, Clients and Elite Political Networks in Mexico.'' Presented at the Comparative Political Networks workshop, Carlos III University, Madrid, June 2015 and Midwest Political Science Association, Chicago, April 2016, and American Sociological Association, Montreal, August 2016.

\item ``A Paradox of Bureaucratic Autonomy: Central bank Legitimacy, Autonomy and Commitment.'' Presented at the Annual Meeting of the American Sociological Association, San Francisco, August 2014.

\item``Accounting for Household Debt: Inequality, Social Policy or Financialization?'' Financialization and its Consequences Conference, Carlos III-Juan March Center for the Social Sciences, Madrid, June 2014.

\item``Washington Dissensus? Ambiguity and Conflict at the International Monetary Fund.'' Presented at the Annual Meeting of the American Sociological Association, New York, August 2013. 

\item``Strategic Transparency: Crisis, Legitimacy and Central Bank Strategies in the Global Diffusion of Inflation Targeting.'' Presented at the Annual Meeting of the Society for the Study of Socio-Economics, Milan, June 2013.

\item``Cycles of contention and settlement: Rethinking the Dynamics of Change in the Macroeconomic Policy Field.'' Presented at the Annual Meeting of the Social Science History Association, Vancouver, November 2012.

\item``A Theory of the Bureaucratic Field: Elite Circulation, Professional Networks and the Policy Process.'' Presented at the 6th Junior Theorists Symposium, Denver, August 2012.

\item``Washington Dissensus? Ambiguity and Conflict at the International Monetary Fund.'' Presented at the Annual Meeting of the American Sociological Association, Denver, August 2012.

\item``Conflict and Consensus among Elite Economists in the State.'' Presented at the 2nd International Sociological Association Forum of Sociology, Buenos Aires, August 2012.

\item``Rethinking the Political Economy of High Inflation: Latin America in the 1980s.'' Presented at the Annual Meeting of the Social Science History Association, Boston, November 2011.

\item``Shifting the Center: Financial Crises and the Transnational Field of Economics.'' Presented at the Annual Meeting of the American Sociological Association, Las Vegas, August 2011.

\item``Network Cohesion and Policy Consensus among Economic Experts.'' Presented at the Annual Meeting of the American Sociological Association, Atlanta, August 2010.

\item``Money and Morality in Early Capitalism: The School of Salamanca's Analysis of Exchange.''  Presented at Politics and Culture: The Third Annual NYLON Conference, London, March 2005.
\end{list}

%\newpage

\sectionhead{Grants and Fellowships}
\begin{tabulary}{.97\textwidth}{@{}p{2.5cm}  L}

2022 & Creative Informatics Small Grant, University of Ediburgh\\
2022 & Principal's Teaching Award Scheme, University of Edinburgh\\
2021 & Creative Informatics PhD Research Assistant grant, University of Edinburgh\\
2009 & Dissertation Improvement Grant, National Science Foundation (\$15,000)\\
2009 & Research Travel Grant, Holtz Center for Science and Technology Studies, University of Wisconsin-Madison (\$1,000)\\
2008 & International Dissertation Research Fellowship, Social Science Research Council (\$25,000)\\
2007 & Dissertation Proposal Development Fellowship, Social Science Research Council (\$5,000)\\
2007 & Summer Research Fellowship, Holtz Center for Science and Technology Studies, University of Wisconsin-Madison (\$3,000)\\
2006 & Research Travel Grant, Holtz Center for Science and Technology Studies, University of Wisconsin-Madison (\$1,000)\\
2004 & Graduate School of Arts and Science Tuition Scholarship, New York University\\ 
\end{tabulary}


\sectionhead{Other awards}
\begin{tabulary}{.97\textwidth}{@{}p{2.5cm}  L}

2012 & American Sociological Association Postdoctoral Fellowship Program (declined)\\
2012 & Honorable mention for ``Cohesion, Consensus and Conflict in Bureaucratic State Elites,'' Ronald S. Burt Student Paper Award from the Economic Sociology Section of the American Sociological Association\\
2008 & Distinction on Preliminary Examination, Sociology of Economic Change and Development\\
2008 & Distinction on Preliminary Examination, Sociology of Science\\
2005 & Gillen Welcome Award, University of Wisconsin-Madison\\
2000 & Eli Chertok Award for excellence in writing a senior thesis in sociology, Department of Sociology, Whitman College\\
\end{tabulary}

\sectionhead{Courses taught}
\begin{list}{\labelitemi}{\leftmargin = 5px}
\item{Sociological theory for Social Research}
\item{Sociology 1a: The Sociological Imagination}
\item{Social Network Research: Theories and Analysis}
\item{Economic Sociology}
\item{Explanation and Understanding}
\item{Finance and Society}
\item{Lecture contributions to: Key Concepts in Digital Sociology, Key Concepts in Global Social Change, Researching Digital Society, Researching Global Social Change, Globalization, Designing and Doing Social Research, Market Design and Policy}
\item{Before 2017: Classical Sociological Theory, Problems of American Racial and Ethnic Minorities, Theories of International Relations (Globalization and Development), Mini-course on Political Networks} 
\end{list}


%\end{tabulary}


%\sectionhead{Teaching Experience}
%\begin{tabulary}{.97\textwidth}{@{}p{2.5cm}  L}

%2015 & Invited instructor: Mini-course on political networks, Centro de Investigaci\'on y Docencia Econ\'omicas (CIDE), Mexico City \\
%2015 & Lecturer: Theories of International Relations (Globalization and Development), IE School of International Relations, Madrid, Spain
 %\emph{--Award for highest student evaluations within department in semester}\\
%2012 & Lecturer: Classical Sociological Theory, University of Wisconsin-Madison\\
%2010 & Lecturer: Problems of American Racial and Ethnic Minorities, University of Wisconsin-Madison\\
%2008 & Lecturer: Problems of American Racial and Ethnic Minorities, University of Wisconsin-Madison\\
%2008 & Teaching Assistant: Survey of Sociology, University of Wisconsin-Madison\\
%2005 & Teaching Assistant: Survey of Sociology, University of Wisconsin-Madison \\
%\end{tabulary}

\sectionhead{Professional Service }
\begin{list}{\labelitemi}{\leftmargin = 5px}
\item Organizer of Futures of Finance and Society conference, University of Edinburgh, December 2018
\item Organizer of workshop on Financial Innovation, Diffusion and Institutionalization: the Case of Securitization, Max Planck Institute for the Study of Societies, Cologne, June 2016
\item Organizer of workshop on Inequality: the Wealth-Credit-Housing Nexus and its Political Consequences, Max Planck-Sciences Po Center on Coping with Instability in Market Societies, April 2016
\item Organizer of Comparative Political Networks conference, Carlos III-Juan March Institute, Madrid, June 2015
\item Jury, Burt Student Paper award, Economic Sociology section of the American Sociological Association, 2015
\item Reviewer for \emph{The American Journal of Sociology, American Sociological Review, American Political Science Review, British Journal of Sociology, Current Sociology,  European Societies, Finance and Society, International Journal of Comparative Sociology, Latin American Politics and Society, Management Science, \OE conomia - History / Methodology / Philosophy, Pol\'itica y Gobierno, Political Studies, Review of International Political Economy, Revista Internacional de Sociologia, Social Forces, Social Network Analysis and Mining, Social Science Research, Socio-Economic Review, Sociological Forum, Sociological Theory, Theory and Society, West European Politics, World Politics}, Routledge, Bristol University Press.
\item Graduate Forum member, New York University, 2005; Organizer and Moderator, Draper Colloquium, New York University, 2003--04 
\end{list}

%\sectionhead{Professional Affiliations}

%\begin{list}{\labelitemi}{\leftmargin = 5px}
%\item American Sociological Association; Social Science History Association; Society for the Study of Socio-Economics
%\end{list}

\sectionhead{Languages}

\begin{list}{\labelitemi}{\leftmargin = 5px}
\item Fluent Spanish; Intermediate French; Basic German
\end{list}

%\sectionhead{References}
%\begin{tabularx}{\textwidth}{@{}XX@{}}
%\\
%Erik Olin Wright (Dissertation chair) & John Levi Martin\\
%Department of Sociology & Department of Sociology\\
%University of Wisconsin-Madison & University of Chicago\\
%8128 Sewell Social Science Building & 1126 East 59th Street\\
%Madison, WI 53706--1393 & (773) 702--7098\\
%(608) 262--0068 & jlmartin@uchicago.edu\\
%wright@ssc.wisc.edu\\
%\\
%Gay Seidman & Joan Fujimura\\
%Department of Sociology & Department of Sociology\\
%University of Wisconsin-Madison & University of Wisconsin-Madison\\
%8128 Sewell Social Science Building & 8128 Sewell Social Science Building\\
%Madison, WI 53706--1393 & Madison, WI 53706--1393\\
%(608) 263--3887 & (608) 265--2724\\
%seidman@ssc.wisc.edu & fujimura@ssc.wisc.edu\\
%\end{tabularx}

\end{document}
